{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-14 documents/acknowledgement.tex
v

Thanks to (Dr. ) Peter Barfuss for spending time reviewing early drafts.

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic nation-state supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca. A special thanks to the dedicated authors that develop and maintain these tools.

Professor Shahramian's excellent video blog {\it The Signal Path} greatly informed this work. Dr. Dainis' videos on microbiological technique were also particularly useful.

@@

Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating midnight ramblings.

@@

@@

The authors acknowledge the IT.IS foundation for doing the same, but actually replying to emails.

>>>>

Thanks to (Dr. ) Barfuss for spending time reviewing an early draft.

This paper would have been absolutely impossible without the support of thousands of open-source software packages, ranging from monolithic state-supported tools like Paraview to poorly-compensated but equally invaluable scripts like zonca. A special thanks to the dedicated authors that develop and maintain these tools.

Professor Shahramian's excellent video blog {\it The Signal Path} greatly informed this work. Dr. Dainis' videos on microbiology were also particularly useful.

@@

Thanks to L.H. for wisdom regarding this project; Profs David and Taylor (among others) at YorkU for being super nice, and H.P. and ice9 for tolerating ramblings.

@@

R.I.P. to Dr. Robert Adair, whose work features prominently here, died Sep. 2020.

@@

The authors acknowledge the IT.IS foundation for doing precisely the same, but actually replying to emails.
